---
title: "Star Wars at Cornell"
format: html
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
#| warning: false
#| message: false
source('SWDataPrep.R')
```

To start, we want to investigate what you did by hand; how many words in each film were positive? How many were negative?

### Counting Sentiments for Each Film

The following code can be run by clicking the green play button on the right.

This first part gets the sentiments from a dictionary, just like you did!

```{r}
sentiments <- 
  SW_movie_scripts |> 
  # This does what you did for each word for every line in the original 3 films
  inner_join(get_sentiments('afinn')) |>
  rename(sentiment = value)

sentiments  |>   filter(movie == "Episode IV")|> 
  slice_head(n=10) |> 
  kable()

```

Now, we can take get the average sentiment per film.
- The group_by function tells R we want our calculations to be by group, rather than overall
- In this case, it tells R we want the mean sentiment for each movie.

```{r}

sentiment_counts <-
  sentiments |> 
  group_by(movie)|>
  summarize(average_sentiment = mean(sentiment)) # Average sentiment for each film

sentiment_counts |> kable()

```

### Visualizing Sentiment for Each Film

```{r}
# Make Plots
ggplot(sentiment_counts,aes(y=movie,x=average_sentiment))+ 
  geom_col() +
  labs(title = "Star Wars Movie Sentiments",
       y = "Movie",x="AFINN Sentiment")
```

### Vader's Conversations

Is Vader such a bad guy? Let's measure his feelings using his words.

We are going to

1) Filter out only Vader's lines from the Episodes IV, V, and VI
2) Get the AFINN sentiment for his words
3) Get an overall average sentiment of his words

### Step 1: Filter out Vader's Lines

### Step 2: Join AFINN sentiments for each of his words

### Step 3: Get the average sentiment of his words


```{r}
#| include: false
#| echo: false
#| eval: false

## Leave this top part as well
SW_movie_scripts |> # Sends the data to the next function


# CODE LINES (copy and past them into the right steps)
  inner_join(get_sentiments('afinn'))|>
  summarize(average_sentiment = mean(value))|>
  filter(character == "Vader")|> # Picks Vader as our character of interest

##### Cut in paste into the correct steps

## STEP 1


## STEP 2


## STEP 3


  kable() # Leave alone

```


### Vaders Sentiment Throughout the Movies

```{r}

SW_movie_scripts |> # Sends the data to the next function
  filter(character == "Vader")|> # Picks Vader as our character of interest
  inner_join(get_sentiments('afinn'))|>
  group_by(movie) |> 
  summarize(average_sentiment = mean(value))|>
  ggplot(aes(x=average_sentiment,y= movie))+
    geom_col(show.legend = F)+
    labs(x = "Contribution to Sentiment",title = "Vaders Conversations",y="")

```

### Are you fighting for the light or embracing the dark side?

Change `chosen_side` with your choice, "light side" or "dark side". It takes a minute to generate.

```{r}
#| warning: false
# replace the quoted text with either `light side` or `dark side`

create_SW_Wordcloud("light side")

```
